sampbias, a method for quantifying geographic sampling biases in species distribution data

### 2020-07-30 appendix_S1.Rmd
changes hyperprior

dat <- read_csv("empirical_analyses/simulations/weight_estimates.csv") %>% 
  mutate(records_area = round(rar / area * 10000, 2)) %>% 
  select(contains("w"), ID, type, records_area) %>% 
    pivot_longer(cols = contains("w_"), names_to = "bias",
                 values_to = "posterior_estimate") %>%
    mutate(bias = gsub("w_", "", .data$bias))
```

>>>>

dat <- read_csv("empirical_analyses/simulations/weight_estimates.csv") %>% 
  mutate(records_area = round(rar / area * 10000, 2)) %>% 
  select(contains("w"), ID, type, records_area) %>% 
  select(-w_rate) %>% 
    pivot_longer(cols = contains("w_"), names_to = "bias",
                 values_to = "posterior_estimate") %>%
    mutate(bias = gsub("w_", "", .data$bias))
```
